%\documentclass{elsarticle}
%%
\documentclass[times,12pt,3p,longtitle]{elsarticle}
\usepackage{makecell}

%%
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

%% Stylefile to load JCOMP template
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{latexsym}
%\journal{Journal of Computational Physics}
\usepackage{amsmath}
\begin{document}

\begin{frontmatter}
\title{A hybrid Eulerian-Lagrangian Vlasov method for nonlinear wave-particle interaction in weakly inhomogeneous magnetic field}
\author[1]{Jiangshan Zheng}

\author[2]{Ge Wang}
\author[1]{Bo Li}
\address[1]{School of Physics, Beihang University, Beijing, Beijing 100191, China}
\address[2]{Institute for Fusion Studies, The University of Texas, Austin, Texas, 78712, USA}
\begin{abstract}
  We present a hybrid Eulerian-Lagrangian Vlasov solver for nonlinear resonant wave-particle interactions problems in weakly inhomogeneous magnetic field.
  The governing Vlasov equation is derived from a recently proposed resonance tracking Hamiltonian method. 
  The method tracks the dynamics of deeply trapped resonant particles in a coherent wave. 
  It gives the evolution of the distribution function with a scale separated Hamiltonian that containing the slowly-varying motion about the resonant frame of reference and fast-varying coherent interactions.
  The hybrid method solves the slowly-varying phase space dynamics by Lagrangian method along the resonant trajectory, while simultaneously manages the fast-varying phase-space evolution in Eulerian grid with an adaptive time step interpolated differential operator scheme.
  We apply our method to study the frequency chirping problem of whistler mode chorus wave in the Earth magnetosphere and successfully reproduce the chirping chorus wave. 
  The results in well agree with previous research. 
  With a focus on nonlinear resonant wave-particle interaction in the weakly inhomogeneous regime, our approach can give high resolution for the fast varying phase space at low computational cost.  
  It could provide additional insights of the wave instabilities and particle energy transfer compared to the conventional Vlasov and particle-in-cell methods.
\end{abstract}
%xtend the periodical condition in the resonance frame
\end{frontmatter}
%\linenumbers

%main text
\clearpage

%intro the wave and the vlasov
\input{cpc/intro}

%our numerical scheme begin with the solver of the following deltaf Vlasov system
%explain the form
%\input{cpc/theory}
\input{cpc/vlasov}

%then we sove the following envelope equation 
%explain the form
%\input{cpc/methods}
\input{cpc/wave}

%the details of the code 
%\input{cpc/results}
\input{cpc/code}

\input{cpc/conclude}

%\input{cpc/appendix}

\bibliographystyle{model1-num-names}
\bibliography{nonlinear_cpc}

\end{document}

%%
